GG_topi2

### 2018-11-07 gg_topi.Rmd
A

sample_data(gg_topi) <- mappingfile
sample_data(gg_topi)$id.topo <- factor(sample_data(gg_topi)$id.topo)
sample_data(gg_topi)$pentatome <- factor(stringr::str_sub(sample_data(gg_topi)$condizione,1,2), labels = c('Pentatoma','Empty'))
sample_data(gg_topi)$bifido <- factor(stringr::str_sub(sample_data(gg_topi)$condizione,3,3), labels = c('Bifido','PBS'))
sample_data(gg_topi)$cond_all <- factor(with(sample_data(gg_topi), paste(timepoint,real_vaccine, real_bifido, sep = '_')))
sample_data(gg_topi)$cond_vac <- factor(with(sample_data(gg_topi), paste(merge_timepoint,real_vaccine, sep = '_')))
sample_data(gg_topi)$cond_bif <- factor(with(sample_data(gg_topi), paste(merge_timepoint,real_bifido, sep = '_')))

@@

## Ordination: Mean all samples per timepoint
```{r}

x <- ordinate(gg_topi, method = "MDS", distance = distwu, weighted = TRUE) %>% plot_ordination(gg_topi, ., justDF = TRUE)

@@

@@

@@

## Differential analysis Pentatome T7 vs not vaccinated T7
```{r}
  res12 <- DESeq2::results(dds, contrast = c("cond_vac","T7_YES","T7_NO"), independentFiltering = TRUE)
  res12.filtered <- res12[!is.na(res12$padj),]
  res12.filtered <- res12.filtered[res12.filtered$padj < threshold,]

>>>>

sample_data(gg_topi) <- mappingfile
sample_data(gg_topi)$id.topo <- factor(sample_data(gg_topi)$id.topo)

sample_data(gg_topi)$pentatome <- factor(stringr::str_split(sample_data(gg_topi)$condizione, ' \\+ ', simplify = TRUE)[,1])
sample_data(gg_topi)$bifido <- factor(stringr::str_split(sample_data(gg_topi)$condizione, ' \\+ ', simplify = TRUE)[,2])

sample_data(gg_topi)$cond_all <- factor(with(sample_data(gg_topi), paste(timepoint,real_vaccine, real_bifido, sep = '_')))
sample_data(gg_topi)$cond_vac <- factor(with(sample_data(gg_topi), paste(merge_timepoint,real_vaccine, sep = '_')))
sample_data(gg_topi)$cond_bif <- factor(with(sample_data(gg_topi), paste(merge_timepoint,real_bifido, sep = '_')))

sample_data(gg_topi)$vacc_bif <- strtoi(paste(ifelse(sample_data(gg_topi)$real_vaccine=='YES','1','0'),ifelse(sample_data(gg_topi)$real_bifido=='YES','1','0'), sep = ''), 2)

@@

## Ordination: Mean all samples per timepoint
```{r}
x <- ordinate(gg_topi, method = "MDS", distance = distwu, weighted = TRUE) %>% plot_ordination(gg_topi, ., justDF = TRUE)

@@

```{r}
ggplot(subset(ordwu, timepoint %in% c('T3','T7'))) +
  geom_point(aes(Axis.1, Axis.2, color=timepoint, shape=bifido), size=3) +
  facet_wrap(pentatome~bifido)+
  theme_bw() 
```

@@

mmtx <- model.matrix(object = ~timepoint*real_vaccine*real_bifido, data = data.frame(gg_topi@sam_data))
idx <- which(apply(mmtx, 2, function(x) all(x==0)))
mmtx <- mmtx[,-idx]

rmmtx <- model.matrix(object = ~ timepoint, data = data.frame(gg_topi@sam_data))

pds <- phyloseq_to_deseq2(ggtopi_filt, design = ~timepoint*real_vaccine*real_bifido, ignoreRank = TRUE)

dds <- DESeq2::DESeq(pds, full = mmtx, reduced = rmmtx, test = 'LRT')

@@

## Differential analysis Pentatome T7 vs not vaccinated T7
```{r}
  res12 <- DESeq2::results(dds, contrast = c("cond_vac","T7_YES","T7_NO"))
  res12 <- DESeq2::results(dds)
  res12.filtered <- res12[!is.na(res12$padj),]
  res12.filtered <- res12.filtered[res12.filtered$padj < threshold,]
